COG-ED Manuscript

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
Kommentar
neuer Kommentar

One task that is often used to investigate effort is the n-back task. <!-- Satz war sehr lang, ich ihn aufgeteilt und etwas umgestellt -->
In this working memory task, a continuous stream of stimuli, e.g. letters, is presented on screen. <!-- zweiter Teilsatz -->
Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six [@Mackworth1959]; and are asked to respond as quickly and as accurately as they can. <!-- dritter Teilsatz-->
It requires simultaneous storage of past stimuli and processing of new stimuli [@Jonides1997]. <!-- Teilsatz nach dem Komma wirkt etwas out of place: der erste Teil beschäftigt sich mit cognitiven Anforderungen an die Teilnehmenden, der zweite aber mit einem Auftrag an die Probanden; Deshalb habe ich den Satz aufgeteilt und den zweiten Teil mit dem ersten verbunden -->
The n-back task is well suited to investigate effort because it is an almost continuous manipulation of task load, as has been shown by monotonic increases in error rates and reaction times [@Jaeggi2010] as well as monotonic increases in brain activity in areas associated with working memory [@Jonides1997; @Owen2005].
However, reliability measures of the n-back task are mixed, presumably due to ceiling effects in performance in the easiest level, causing inconsistent associations of n-back performance and measures such as executive functioning and fluid intelligence [@Jaeggi2010].

A way to quantify the subjective cost of each n-back level has been developed by Westbrook et al. [-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
First, the participants complete n-back level one to six to familiarize themselves with the task.
Then, each level two to six is being compared with level one by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for level one.
If they choose the more difficult level, the reward for level one increases by 0.50\$, if the choose level one, it decreases by 0.50\$.
This is repeated five more times, with each adjustment of the level one reward being half as big as in the previous step, while the reward for the more difficult level remains fixed at 2\$.
The idea is to estimate the participants' subjective cost of the more difficult level by identifying the smallest reward they would still be okay with being paid for doing level one.
Therefore, the higher the difficult level, the smaller the reward that the participants would accept for level one.
The subjective value (SV) of each difficult level is then calculated by dividing the final reward value of level one by the fixed 2\$ reward of the more difficult level.
Westbrook et al. [-@Westbrook2013] used these SVs to investigate interindividual differences in effort discounting by plotting the SVs and computing an area under the curve (AUC).
Younger participants had a larger AUC than older participants, i.e. they needed a lower monetary incentive for choosing the more difficult levels over level one.

>>>>

One task that is often used to investigate effort is the n-back task. <!-- Satz war sehr lang, ich ihn aufgeteilt und etwas umgestellt -->
In this working memory task, a continuous stream of stimuli, e.g. letters, is presented on screen. <!-- zweiter Teilsatz -->
Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six [@Mackworth1959]; and are asked to respond as quickly and as accurately as they can. <!-- dritter Teilsatz-->
It requires simultaneous storage of past stimuli and processing of new stimuli [@Jonides1997]. <!-- Teilsatz nach dem Komma wirkt etwas out of place: der erste Teil beschäftigt sich mit cognitiven Anforderungen an die Teilnehmenden, der zweite aber mit einem Auftrag an die Probanden; Deshalb habe ich den Satz aufgeteilt und den zweiten Teil mit dem ersten verbunden -->
The n-back task is well suited to investigate effort because it is an almost continuous manipulation of task load, as has been shown by monotonic increases in error rates and reaction times [@Jaeggi2010] as well as monotonic increases in brain activity in areas associated with working memory [@Jonides1997; @Owen2005].
However, reliability measures of the n-back task are mixed, presumably due to ceiling effects in performance in the easiest level, causing inconsistent associations of n-back performance and measures such as executive functioning and fluid intelligence [@Jaeggi2010]. <!-- Ist hier als Reliabilität die Korrelation zum Außenkriterium gemeint (EF und gf?); Falls nicht, wären doch fehlende Reliabilitäten und Korrelationen zwei verschiedene Punkte-->

A way to quantify the subjective cost of each n-back level has been developed by Westbrook et al. [-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED). <!-- gibt es keine Möglichkeit, die Quelle automatisiert pasten zu lassen? Sonst müsste man an der Stelle auch zuerst alle drei Autoren nennen, oder?  -->
First, the participants complete n-back level one to six to familiarize themselves with the task.
Then, each level two to six is being compared with level one by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for level one.
If they choose the more difficult level, the reward for level one increases by 0.50\$, if the choose level one, it decreases by 0.50\$.
This is repeated five more times, with each adjustment of the level one reward being half as big as in the previous step, while the reward for the more difficult level remains fixed at 2\$.
The idea is to estimate the participants' subjective cost of the more difficult level by identifying the smallest reward they would still be okay with being paid for doing level one.
Therefore, the higher the difficult level, the smaller the reward that the participants would accept for level one.
The subjective value (SV) of each difficult level is then calculated by dividing the final reward value of level one by the fixed 2\$ reward of the more difficult level.
Westbrook et al. [-@Westbrook2013] used these SVs to investigate interindividual differences in effort discounting by plotting the SVs and computing an area under the curve (AUC).
Younger participants had a larger AUC than older participants, i.e. they needed a lower monetary incentive for choosing the more difficult levels over level one.
